Sequential rank agreement methods for comparison of ranked lists

### 2015-05-23 latex/paper.Rnw
Implementing generic function

@@

\title{Sequential rank agreement methods for comparison of ranked
  lists}
\author{Claus Thorn Ekstrøm}
\author{Thomas Alexander Gerds}
\author{Kasper Brink-Jensen}
\affil{Biostatistics, University of Copenhagen}

@@

producelists <- function(x, y) {
    nitems <- ncol(x)
    index <- seq(1, nrow(golub))
                                        # d <- data.frame(y, x)

>>>>

%%% RSS specific items

\title[Sequential rank agreement]{Sequential rank agreement methods for comparison of ranked
  lists}
\author[Ekstrøm {\it et al.}]{Claus Thorn Ekstrøm}
\address{Affiliation,
City,
Country.}
\email{Author@emailaddress.com}
\author{Thomas Alexander Gerds}
\address{Affiliation,
City,
Country.}
\author{Andreas Kryger Jensen}
\address{Affiliation,
City,
Country.}
\author{Kasper Brink-Jensen}
\address{Affiliation,
City,
Country.}

@@

% \title{Sequential rank agreement methods for comparison of ranked
  lists}
% \author{Claus Thorn Ekstrøm}
% \author{Thomas Alexander Gerds}
% \author{Kasper Brink-Jensen}
% \affil{Biostatistics, University of Copenhagen}

@@

producelists <- function(x, y) {
    nitems <- nrow(x)
    index <- seq(1, nrow(golub))
                                        # d <- data.frame(y, x)
